%-------------------------
% Resume in Latex
% Author : Valentina Galeano
% Based off of: https://github.com/valegal/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://valentinagaleano.com/}{\Large Valentina Galeanoj}} & Email : \href{mailto:valentinagaleanocastro1@gmail.com}{valentinagalena1@gmail.com}\\
%   \href{httsp://valentinagaleano.com/}{http://www.valentinagaleano.com} & Mobile : +57-300-250-6261 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Valentina Galeano Castro} \\ \vspace{1pt}
    \small +57 3002506261 $|$ \href{mailto:x@x.com}{\underline{valentinagalena1@gmail.com}} $|$ 
    \href{https://linkedin.com/in/valegal}{\underline{linkedin.com/in/valegal}} $|$
    \href{https://github.com/valegal}{\underline{github.com/valegal}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Industrial University of Santander}{Bucaramanga, Colombia GMT-5}
      {Bachelor's Degree in Software Engineering}{January 2019 -- Present}
    \resumeSubheading
      {Google Cybersecurity Professional Certificate}{Colnodo, Remote}
      {Google Career Certificates}{October 2023 -- April 2024}
      \resumeSubheading
      {The Complete Web Development Bootcamp
}{Udemy Certificates}
      {Dr. Angela Yu, Developer and Lead Instructor}{May 2022 -- September 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}

  \resumeSubHeadingListStart

     \resumeSubheading
      {Full Stack Developer}{January 2021 -- February 2023}
      {(DSI) Information Systems Division, Industrial University of Santander}{Full-Time}
      \resumeItemListStart
        \resumeItem{Developed backend and frontend modules for a large-scale project using SCRUM.}
        \resumeItem{Implemented interactive tables and user interfaces with Angular CLI, Angular Material, and Angular 17; utilized the MVC pattern with Java, SpringBoot, and Rest APIs.}
        \resumeItem{Collaborated with the team to ensure timely delivery and product quality using test-driven development.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Software Engineer}{April 2023 -- Present}
      {Various SMEs and Clients}{Freelance}
      \resumeItemListStart
        \resumeItem{Developed a REST API using FastAPI and PostgreSQL to manage data from learning management systems.}
        \resumeItem{Designed software architecture and intuitive interfaces using React, Strapi, MySQL, Firebase, and Next.js.}
        \resumeItem{Built a full-stack web application using NodeJS, React, PostgreSQL, and Docker to analyze GitHub data.}
      \resumeItemListEnd


    \resumeSubHeadingListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
        {\textbf{Grivp Data System} $|$ \emph{JavaScript, Node.js, Express, React, MySQL, Nginx, Docker}}{February 2024 -- July 2024}
        \resumeItemListStart
          \resumeItem{Developed a full-stack web application with Node.js serving a REST API, and React as the frontend.}
          \resumeItem{Implemented JWT and Cookies for secure authentication and authorization.}
          \resumeItem{Visualized data collected by Raspberry Pi routines, stored on a local server, accessible via a web platform deployed on Nginx.}
        \resumeItemListEnd


    \resumeProjectHeading
        {\textbf{Cloud-Based Inventory Management Platform}}{June 2021 -- Present}
        \resumeItemListStart
          \resumeItem{Developed a scalable platform for real-time stock tracking across multiple locations using .NET Core.}
          \resumeItem{Implemented Azure Functions for efficient asynchronous task processing and Azure SQL Database for secure data storage.}
          \resumeItem{Collaborated with stakeholders to gather requirements and ensure alignment with business goals.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{CI/CD Pipeline for Logistics Product}}{March 2021 -- October 2023}
        \resumeItemListStart
          \resumeItem{Built and maintained a CI/CD pipeline for a logistics product using Jenkins and GitHub Actions, automating the build, testing, and deployment processes.}
          \resumeItem{Containerized the application using Docker and deployed it on AWS, leveraging Terraform for scalable and reliable infrastructure management.}
          \resumeItem{Facilitated cross-functional team collaboration to integrate continuous feedback, enhancing the product’s efficiency and reliability. Led sprint reviews and retrospectives}
        \resumeItemListEnd


    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS, Ruby, .NET} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, Express, Flask, JUnit, WordPress, Material-UI, Angular, FastAPI, .NET Core} \\
     \textbf{Developer Tools \& Libraries}{: Git, Docker, Kubernetes, Travis CI, Google Cloud Platform, VS Code, TensorFlow, PyCharm, IntelliJ, Eclipse, Pandas, NumPy, Matplotlib, AWS, Terraform, Jenkins, Azure.} \\
     \textbf{Languages}{: English, Spanish.}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}
